### 2018-01-27 Sections/essay_the_economics_of_the_quantum_internet.tex
Added epilogue stub

Technology should benefit humanity, not only an elite few --- \textit{Homo sum humani a me nihil alienum puto}. In light of this, who exactly will benefit from the quantum internet? Its beauty is that it doesn't create a system of winners and losers. Rather, it establishes a technological infrastructure from which all can benefit, rich or poor. Well-resourced operators who can afford quantum computers, for example, will benefit from being able to license out compute time on their computers, ensuring no wasted clock-cycles and maximising efficiency. The less-well-resourced will benefit in that they will have a means by which to access the extraordinary power of quantum computing on a licensed basis, facilitating access to infrastructure by those who otherwise would have been priced out of the market. This is essentially the same model as what is employed by some present-day supercomputer operators, enabling small players access to supercomputing infrastructure. The quantum internet is critical to achieving the same goal in the quantum era. This could have transformative effects on the developing world in particular. And many emerging industries, for whom access to quantum computation will be critical, but who cannot afford them, will benefit immensely from the client/server model.

@@

The future quantum economy might be made more efficient by artificially transferring capital from low-multiplier sectors to high-multiplier quantum technologies. Or maybe the market will do this on its own accord\footnote{Have faith in the invisible hand.}? This is a uniquely quantum consideration that never previously applied to conventional supercomputing. The onset of the quantum era may redefine our entire economic mindset and fiscal policy-making, to adapt to the unique economic idiosyncrasies of this emerging technology.

>>>>

Technology should benefit humanity, not only an elite few \latinquote{Homo sum humani a me nihil alienum puto}. In light of this, who exactly will benefit from the quantum internet? Its beauty is that it doesn't create a system of winners and losers. Rather, it establishes a technological infrastructure from which all can benefit, rich or poor. Well-resourced operators who can afford quantum computers, for example, will benefit from being able to license out compute time on their computers, ensuring no wasted clock-cycles and maximising efficiency. The less-well-resourced will benefit in that they will have a means by which to access the extraordinary power of quantum computing on a licensed basis, facilitating access to infrastructure by those who otherwise would have been priced out of the market. This is essentially the same model as what is employed by some present-day supercomputer operators, enabling small players access to supercomputing infrastructure. The quantum internet is critical to achieving the same goal in the quantum era. This could have transformative effects on the developing world in particular. And many emerging industries, for whom access to quantum computation will be critical, but who cannot afford them, will benefit immensely from the client/server model.

@@

The future quantum economy might be made more efficient by artificially transferring capital from low-multiplier sectors to high-multiplier quantum technologies. Or maybe the market will do this on its own accord\footnote{Have faith in the invisible hand.}? This is a uniquely quantum consideration that never previously applied to conventional supercomputing\index{Supercomputers}. The onset of the quantum era may redefine our entire economic mindset and fiscal policy-making, to adapt to the unique economic idiosyncrasies of this emerging technology.
